\documentclass[letter]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{latexsym}
\usepackage[pdftex]{graphicx}
\usepackage{color}

\setlength{\topmargin}{-0.5in} \setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0.0in} \setlength{\textheight}{9.1in}

\newlength{\pagewidth}
\setlength{\pagewidth}{6.5in} \pagestyle{empty}

\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newenvironment{problem}[1][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\title{Zorich Chapter 2: The Real Numbers Notes}
\date{}

\begin{document}
\maketitle
\vspace{-.5in}

\begin{problem}[Problem 1]
The Fibonacci sequence is defined as follows: $F_1=F_2=1$, and for
$n>2$, $F_n=F_{n-1}+F_{n-2}$.  What is $F_n\bmod 2$?  Prove your
answer.
\end{problem}

\begin{problem}[Problem 2]
Prove that $\Sigma_{i=1}^{n}i^3=\left[\frac{n(n+1)}{2}\right]^2$.
\end{problem}

\begin{problem}[Problem 3]
Prove that, if $x\not=1$, then $\Sigma_{i=0}^{n}x^i=\frac{x^{n+1}-1}{x-1}$.
\end{problem}

\begin{problem}[Problem 4]
Let $x_1=\sqrt{1+1}$ and define $x_n=\sqrt{1+x_{n-1}}$ for all $n>1$.
Prove that $x_i$ is irrational for all $i$.  You may assume that
$\sqrt{2}$ is irrational.
\end{problem}


\begin{problem}[Problem 5]
Consider a tournament of $n$ teams in which each team plays every
other team exactly once.  Show that after the tournament completes, we
can always arrange the teams in some order $T_1, \ldots, T_n$ such
that $T_i$ beat $T_{i-1}$ for all $2\leq i\leq n$.
\end{problem}


\begin{problem}[Problem 6]
Consider the following game.  The game begins with several piles of
tokens between the players, and each player has an unlimited supply of
tokens.  The players take turns and, on their turn, a player can take
1 token from a pile, say pile $i$, and may place any number of tokens
on the piles to the left of pile $i$.  The winner is the player that
draws the last token.  Prove that the game must eventually end.

More precisely, the game begins with $n$ piles of coins.  On each
turn, the current player selects a non-empty pile $i$ and removes one
token from that pile and places tokens on piles $j>i$.  Players cannot
create new piles.
\end{problem}



\end{document}
\theend
